Backward Population Synthesis: Mapping the Evolutionary History of Gravitational-Wave Progenitors

### 2022-06-04 src/tex/ms.tex
Grammar edit up to figure 4

\begin{figure}
\includegraphics[width=0.49\textwidth]{figures/GWTC-3_f_acc_mass.pdf}
\caption{
    The posterior density in the $m_{1,{\rm GW}}-f_{\rm acc}$ space for most of the events in GWTC-3.
    Note that $m_{1,{\rm GW}}$ here refers to the reprojected posterior instead of the posterior released by LIGO.
    Each contour is the $68\%$ credible interval of the posterior density for a particular event.
    At $m_{1,{\rm GW}} \sim 45 M_{\odot}$, the pair instability supernova mechanism prevents \texttt{COSMIC} from producing events that are more massive than this cutoff.
    Therefore, events with the majority of posterior support above this cutoff is not compatible with \texttt{COSMIC}, hence has a large KL divergence and excluded from this figure.
    On the low mass end, neutron star binaries or neutron star-black hole binaries are subjected to randomness induced by the natal kick,
    also resulting in a larger and fluctuating KL divergence, therefore they are also excluded from the analysis.
}
\label{fig:GWTC-3_f_acc_mass}
\script{figure4_population.py}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.49\textwidth]{figures/GWTC-3_f_acc_mass.pdf}
\caption{
    The posterior density in the $m_{1,{\rm GW}}-f_{\rm acc}$ space for most of the events in GWTC-3.
    Note that $m_{1,{\rm GW}}$ here refers to the reprojected posterior instead of the posterior released by LIGO.
    Each contour is the $68\%$ credible interval of the posterior density for a particular event.
    At $m_{1,{\rm GW}} \sim 45 M_{\odot}$, the pair instability supernova mechanism prevents \texttt{COSMIC} from producing events that are more massive than this cutoff.
    Therefore, events with the majority of posterior support above this cutoff are not compatible with \texttt{COSMIC}, hence have a large KL divergence and are excluded from this figure.
    On the low mass end, neutron star binaries or neutron star-black hole binaries are subjected to randomness induced by the natal kick,
    also resulting in a larger and fluctuating KL divergences, and therefore are also excluded from the analysis.
}
\label{fig:GWTC-3_f_acc_mass}
\script{figure4_population.py}
\end{figure}
